---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# strr

<!-- badges: start -->
<!-- badges: end -->

Tools for analysis of short-term rental data.

- Clean and process raw AirDNA data files.
- Compress and expand tables of STR data.
- Generate reliable statistical estimates of STR listings' actual locations.
- Identify commercial STR operations.
- Identify frequently rented entire-home listings.
- Identify "ghost hostels"--clusters of private-room listings operated out of a single housing unit.
- Identify STR listings which are located in actual housing units.

## Installation

You can install the released version of strr from [CRAN](https://CRAN.R-project.org) with (This is not currently working, since the package has not yet been submitted to CRAN.):

``` r
install.packages("strr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("UPGo-McGill/strr")
```

## strr_process_*: Cleaning and processing raw AirDNA data files

TKTK

```{r example}
library(strr)
## basic example code
```


## strr_multi: Identifying commercial STR operations

TKTK


## strr_compress and strr_expand: Compressing and expanding tables of STR data

TKTK


## strr_raffle: Generating reliable estimates of STR listing locations

TKTK

## strr_FREH: Identifying frequently rented entire-home STRs

TKTK

## strr_ghost: Identifying clusters of private-room listings operated out of a single housing unit

TKTK

## strr_housing: Identifying STR listings located in actual housing units

TKTK


## Data usage

Most of the functions in strr are designed to work with raw data from AirDNA: either the `property` files which contain one entry per listing, or the `daily` files which contain one entry per listing per day. TKTK

